Depth sample comparison

### 2019-11-02 code/depth_comparison.Rmd
ordered otus

```{r}
ggplot(rbcl_1, aes(x=top_sample, y=rel_abund, fill = otu_name))+
  geom_bar(stat="identity") +
  facet_grid(rows = vars(depth_chr %>% fct_relevel("surface","sub-surface"))) +
  labs(x="Sample ID", y="Relative abundance", fill="OTU")
```

@@

>>>>

```{r}

otu_ord <- c("Chlainomonas A","Sanguina B", "Other Chloromonas","Chloromonas krienitzii","Chloromonas muramotoi C","Chloromonas D", "Algae E","Chloromonas F", "Trebouxiophyceae G")

depth <- ggplot(rbcl_1, aes(x=top_sample, y=rel_abund, fill = otu_name %>% fct_relevel(otu_ord)))+
  geom_bar(stat="identity") +
  facet_grid(rows = vars(depth_chr %>% fct_relevel("surface","sub-surface"))) +
  labs(x="Sample ID", y="Relative abundance", fill="OTU", tag="D")
depth
```

@@

```{r output, include=FALSE}
ggsave(filename = here("manuscript/figs/4_depth_comparison/rbcl.pdf"), plot=depth)
```
